A Toolbox for Manipulating and Assessing Color Palettes

### 2019-07-11 pkg/colorspace/paper/Toolbox/slides.Rnw
small tweak
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@496 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
shorter title without 'for Statistical Graphics'
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@498 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\title{A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics}
\subtitle{\phantom{.}\\Achim Zeileis, Jason C. Fisher, Kurt Hornik, Ross Ihaka, Claire D. McWhite, Paul Murrell, Reto Stauffer, Claus O. Wilke}
\author{\vspace*{-6.83cm}\hspace*{12.5cm}\includegraphics[width=1.6cm]{palmfooter.png}\\[5.5cm]}
\URL{http://colorspace.R-Forge.R-project.org/}

@@

\section{colorspace: A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics}

@@

\begin{frame}
\frametitle{Base R}

>>>>

\title{A Toolbox for Manipulating and Assessing Color Palettes}
\subtitle{\phantom{.}\\Achim Zeileis, Jason C. Fisher, Kurt Hornik, Ross Ihaka, Claire D. McWhite, Paul Murrell, Reto Stauffer, Claus O. Wilke}
\author{\vspace*{-6.3cm}\hspace*{12.5cm}\includegraphics[width=1.6cm]{palmfooter.png}\\[5.5cm]} %% -6.83 with "for Statistical Graphics"
\URL{http://colorspace.R-Forge.R-project.org/}

@@

\section{colorspace: A Toolbox for Manipulating and Assessing Color Palettes}

@@

\begin{frame}
\frametitle{Base R\only<2>{: Why you might not need our package after all}}
